\LARGE \bf On the use of vehicle categorization and context information for messages forwarding in VANETs

### 2016-12-19 paperITSC.tex
axes => axles

We consider a scenario where vehicles create messages to be forwarded for a globally known fixed infrastructure. However, to deliver these messages, intelligent forwarding decisions are required. In this regard, our protocol uses three different schemes, i.e., vehicle distance to the destination, vehicle speed, and its category. Additionally, we used a mechanism called \emph{RateTimeToSend} which uses traffic flow information to control message forwarding rate. To evaluate the performance of our protocol, we performed an extensive set of simulations by considering different parameters.

@@

An example of a network that could make use of context information are the opportunistic networks, which take advantage of opportunistic encounters (not scheduled) to exchange data and share contextual information  \cite{geoopp2014}. Being aware of its neighbors and message destination position, a node can forward incoming messages towards the destination, by selecting the node that is geographically closer to the destination \cite{gpsr2000}. This way, the message could be forwarded accurately by using information about immediate neighbors only \cite{magf2009}.

@@

In this section, we explain the use of ontologies for vehicles categorization.

Ontology is an organized form of representing the data. It is used to represent different kinds of objects and show the relationship among them. It provides a common vocabulary to enable interoperability, resolve ambiguity and hence to describe concepts and the relations that exist between them \cite{madkour2011}.

@@

For our work, we used the ontology\footnote{Draft available on (http://auto.sdo-gao.appspot.com/) Access in: 14 June 2016} proposed in \cite{gao_2016} that categorizes the vehicle according to its physical features (e.g., size of the vehicle, the number of axes) to represent the vehicles categories. Furthermore, we also need to categorize the vehicles by its usage (i.e., private car, taxi). Therefore, we have added in the ``\emph{CarUsageType}'' a vehicle usage category. This category defines how the vehicle will be used and allows the extraction of mobility patterns information. The physical category should be used by traffic management companies, for instance, in the toll collection. While, the usage category can be used by forwarding protocols to decide which node is the best to carry a message. In our protocol, the vehicle usage category information is sent by vehicles, along with other information collected from sensors.

@@

For network and transport layers, we used WAVE Short Message Protocol (WSMP) standard. We have adopted the IEEE 802.11p standard protocol for the PHY and MAC layers. For multichannel operation, we used the IEEE 1609.4 standard protocol. The signal propagation was made according to the Simplified Path-Loss model, described in \cite{tse2005}.

>>>>

We consider a scenario where vehicles create messages to be forwarded for a globally known fixed infrastructure. However, to deliver these messages, intelligent forwarding decisions are required. In this regard, our protocol uses three different schemes, i.e., vehicle distance to the destination, vehicle speed, and its category. Additionally, we used a novel mechanism called \emph{RateTimeToSend} which uses traffic flow information to control message forwarding rate. To evaluate the performance of our protocol, we performed an extensive set of simulations by considering different parameters.

@@

An example of a network that could make use of context information are the opportunistic networks, which take advantage of opportunistic encounters (not scheduled) to exchange data and share contextual information  \cite{geoopp2014}. Being aware of its neighbors and message destination position, a node (vehicle) can forward incoming messages towards the destination, by selecting the node that is geographically closer to the destination \cite{gpsr2000}. This way, the message could be forwarded accurately by using information about immediate neighbors only \cite{magf2009}.

@@

In this section, we explain the use of ontologies for vehicles categorization. Ontology is an organized form of representing the data. It is used to represent different kinds of objects and show the relationship among them. It provides a common vocabulary to enable interoperability, resolve ambiguity and hence to describe concepts and the relations that exist between them \cite{madkour2011}.

@@

For our work, we used the ontology\footnote{Draft available on (http://auto.sdo-gao.appspot.com/) Access in: 17 October 2016} proposed in \cite{gao_2016} that categorizes the vehicle according to its physical features (e.g., size of the vehicle, the number of axles), generating the \emph{physical category}. Furthermore, we also need to categorize the vehicles by its usage (i.e., private car, taxi, bus). Therefore, we have added in the ``\emph{CarUsageType}'' a vehicle \emph{usage category}.
This category defines how the vehicle will be used and allows the extraction of mobility patterns information. The \emph{physical category} should be used by traffic management companies, for instance, in the toll collection. While, the \emph{usage category} can be used by forwarding protocols to decide which node is the best to carry a message. In our protocol, the vehicle \emph{usage category} information is sent by vehicles, along with other information collected from sensors.

@@

For network and transport layers, we used WAVE Short Message Protocol (WSMP) standard. We have adopted the IEEE 802.11p standard protocol for the PHY and MAC layers. We used the IEEE 1609.4 standard protocol for channel operation. This standard define two types of channel, the Control Channel (CCH) and the Service Channel (SCH). In your simulation all communication is through the service channel SCH1 174. The signal propagation was made according to the Simplified Path-Loss model, described in \cite{tse2005}.
